Understanding the Lomb-Scargle Periodogram

### 2017-01-09 PracticalLombScargle.tex
Add failure modes figure

$P(f)$ from \eq{lomb-scargle-periodogram}

\begin{equation}
  p(f~|~D) \propto e^{-n \chi^2 / 2} \propto e^{P(f)}
\end{equation}

@@

@@

All periodograms in this paper were computed using the Astropy
implementation of the \citet{Press89}, \citet{Zechmeister09}, and
\citet{Palmer09} algorithms, which was adapted from Python code originally
published by \citet{ICVG2014} and \citet{VanderPlas2015}.
All code for this paper is available in the form of Jupyter notebooks on the
author's GitHub repository\footnote{\url{http://github.com/jakevdp/PracticalLombScargle}}

>>>>

For the standard model, the Bayesian periodogram is given by
\begin{equation}
  p(f~|~D) \propto e^{-N \chi^2 / 2} \propto e^{P_{LS}(f)}
  \eqlabel{bayesian-periodogram}
\end{equation}
where $P_{LS}(f)$ is the Lomb-Scargle power from \eq{lomb-scargle-periodogram}.
The effect of this exponentiation, as seen in \fig{bayesian-periodogram},
is to suppress all peaks in relation to the largest one of the spectrum.

@@

\subsection{Failure Modes}
\sectlabel{failure-modes}

When using the Lomb-Scargle periodogram in an observational pipeline, it is
vital to keep in mind the failure modes of the periodogram approach, which
are rooted in the aliasing and pseudo-aliasing effects discussed in
\sect{window-functions}.
Due to the interaction of the signal, the convolution due to the survey window,
and noise in the data, it is quite common for the largest peak in the
periodogram to correspond not to the true frequency, but some alias of that
frequency.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig25_failure_modes}
  \caption{Comparison of the true period and peak Lomb-Scargle period for
    1000 simulated periodic light curves.
    Each has 60 irregular observations over 180 nights,
    with a cadence typical of ground-based surveys ({i.e.} showing a strong
    diurnal window pattern similar to \fig{LINEAR-window}).
    The Lomb-Scargle peak does not always coincide with the true period,
    and there is noticeable structure among these failures.
    Panels (a)-(d) show some of the failure modes we can expect due to this
    window function; see the text for more discussion.
    \figlabel{failure-modes}}
\end{figure}

\todo{Detailed discussion of \fig{failure-modes}
\citep[see, e.g.][]{VanderPlas2015, Long2016}

@@

All periodograms in this paper were computed using the Astropy
implementations of the \citet{Press89}, \citet{Zechmeister09}, and
\citet{Palmer09} algorithms, which were adapted from Python code originally
published by \citet{ICVG2014} and \citet{VanderPlas2015}.
All code for this paper is available in the form of Jupyter notebooks in the
paper's GitHub repository\footnote{\url{http://github.com/jakevdp/PracticalLombScargle}}
